Open Split Tests

### 2021-06-21 inst/rmd/opensplittests.Rmd
Minor fixes
Fix errors

@@

```{r}
df <- get_hgis_data(here("data/USAMS052621R.txt"), as.Date("2021-06-04")) #, standards)
```

@@

```{r}
df %>% 
  filter(!(Pos %in% 1:4)) %>% 
  plot_hgis_time(normFm, ce*normFm) +
  ggtitle("Sample ratio vs. time")
```

```{r}
df %>% 
  filter(!(Pos %in% 1:4)) %>% 
  plot_hgis_time(he12C) +
  ggtitle("Sample current vs time")
```

@@

```{r}
df_sum %>% 
  filter(as.numeric(Pos) > 4) %>% 
  mutate(sig_normFm = max_err * normFm) %>% 
  select(Pos, Sample.Name, he12C, n_runs, norm_ratio, sig_norm_ratio) %>% 
  arrange(Sample.Name)
```

```{r}
df_sum %>% 
  filter(as.numeric(Pos) > 4) %>% 
  ggplot(aes(Sample.Name, norm_ratio)) +
    geom_pointrange(aes(ymin = norm_ratio - sig_norm_ratio, ymax = norm_ratio + sig_norm_ratio),
                    size = .5) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1)) +
      labs(x = NULL,
           y = "Fraction Modern")
plot_hgis_summary()
```

@@

```{r}
df_sum %>% 
  filter(as.numeric(Pos) > 4) %>% 
  compare_replicates()
```

@@

```{r}
df_sum %>% 
  filter(as.numeric(Pos) > 4,
         !is.na(fm_consensus)) %>% 
  select(Sample.Name, fm_consensus, norm_ratio, sig_norm_ratio) %>% 
  mutate(Fm_diff = norm_ratio - fm_consensus,
         sigma = amstools::sigma(norm_ratio, fm_consensus, sig_norm_ratio)) %>% 
  arrange(Sample.Name)
```

@@

write_csv(carb_data, here("data/carb_data_2021-06-04.csv"))
insert_samples(carb_data)
carb_data
```

>>>>

ds[-(1:4),-4]
```

@@

```{r}
df <- process_hgis_results(here("data/USAMS052621R.txt"), as.Date("2021-06-04")) #, standards)
```

@@

```{r}
df %>% 
  filter(!(pos %in% 1:4)) %>% 
  plot_hgis_time(norm_ratio, sig_norm_ratio) +
  ggtitle("Sample ratio vs. time")
```

```{r}
df %>% 
  filter(!(pos %in% 1:4)) %>% 
  plot_hgis_time(he12C) +
  ggtitle("Sample current vs time")
```

@@

```{r}
df_sum %>% 
  filter(as.numeric(pos) > 4) %>% 
  select(pos, sample_name, he12C, n_runs, norm_ratio, sig_norm_ratio) %>% 
  arrange(sample_name)
```

```{r}
df_sum %>% 
  filter(as.numeric(pos) > 4) %>% 
  ggplot(aes(sample_name, norm_ratio)) +
    geom_pointrange(aes(ymin = norm_ratio - sig_norm_ratio, ymax = norm_ratio + sig_norm_ratio),
                    size = .5) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1)) +
      labs(x = NULL,
           y = "Fraction Modern")
```

@@

```{r}
df_sum %>% 
  filter(as.numeric(pos) > 4) %>% 
  compare_replicates()
```

@@

```{r}
df_sum %>% 
  filter(as.numeric(pos) > 4,
         !is.na(fm_consensus)) %>% 
  select(sample_name, fm_consensus, norm_ratio, sig_norm_ratio) %>% 
  mutate(Fm_diff = norm_ratio - fm_consensus,
         sigma = amstools::sigma(norm_ratio, fm_consensus, sig_norm_ratio)) %>% 
  arrange(sample_name)
```

@@

write_csv(carb_data, here("data/carb_data_2021-06-04.csv"))
#insert_samples(carb_data)
carb_data
```
